\thispagestyle{empty}
\noindent
{\rm\sf\bfseries SHIVAPADA RATNAKOSHA}\\[5pt]
{\rm (Veerashaiva-Lingayata Paribhashika Padakosha)} 

\noindent
{\rm Edited by Editorial Committee}\\
{\rm Honorary Editor : Jagadguru Sri Shivarathri Deshikendra Mahaswamigalu}\\
{\rm Executive Editor : Dr. Nandeesh Hanchye}\\
{\rm Published by JSS Granthamale, Mysuru 570 004}\\[8pt]
{\rm Pages : xl + 896}

\vspace{1cm}

\noindent
{\rm \copyright \ Publishers}\\[7pt]
{\rm First Edition : 2020}\\[7pt]
{\rm No. of Copies : 2000}\\[7pt]
{\rm Price : \rupee\,1,000}

\bigskip

\noindent
{\rm Typeset by : Sriranga Digital Software Technologies Pvt. Ltd., Srirangapattana}

\medskip

\noindent
{\rm Printed at : Lakshmi Printers, Bengaluru.}

\vfill

\noindent
{\bf AthiRka neravu : kananxDa matutx saMsakxqqti ilAKe, kanARTaka sakARra}

\vskip 1cm

\noindent
{\bf\large shivapada ratanxkoVsha}\\[5pt]
(viVrasheYva-liMgAyata pAriBASika padakoVsha) 

\smallskip

\noindent
saMpAdane : saMpAdaka samiti\\
gwrava saMpAdakaru : jagadugxru shirxV shivarAtirx deVshikeVMdarx mahAsAvxmigaLavaru\\
kAyaRnivARhaka saMpAdakaru : DA. naMdiVshf haMce\\
parxkaTaNe : je{esf}{esf} \ garxMthamAle, meYsUru 570 004\\[8pt]
puTagaLu : {\rm xl} + 896

\vspace{1cm}

\noindent
{\rm \copyright} parxkAshakaru\\[7pt]
parxthama mudarxNa : 2020\\[7pt]
parxtigaLu : 2000\\[10pt]
bele : \rupee\,1,000

\bigskip

\noindent
akaSxra joVDaNe : shirxVraMga DijiTalf sAPfTxveVrf TekAnxlajiVsf, perxY. li., shirxVraMgapaTaTxNa

\medskip

\noindent
mudarxkaru : lakiSxmXV mudarxNAlaya, beMgaLUru

\newpage

\thispagestyle{empty}

\phantom{a}

\vfill

\begin{center}


{\Large\bf gwrava saMpAdakaru}\\

\medskip

{\large paramapUjayx jagadugxru shirxV shivarAtirx deVshikeVMdarx mahAsAvxmigaLavaru}

\vskip 1cm

{\Large\bf kAyaRnivARhaka saMpAdakaru}

\medskip

{\fontsize{14pt}{16pt}\selectfont
DA. naMdiVshf haMce}\relax

\vskip 1cm


{\Large\bf saMpAdaka samiti}

\bigskip
\medskip

{\fontsize{14pt}{16pt}\selectfont
porx. ji.esf. sidadhxliMgayayx\\[8pt]
DA. Ti.vi. veMkaTAcala shAsitxrXV\\[8pt]
DA. enf.esf. tArAnAtha\\[8pt]
vidAvxnf DA. ecf.vi. nAgarAjarAvf\\[8pt]
vidAvxnf DA. si. shivakumArasAvxmi\\[8pt]
shirxV Arf.esf. pUNARnaMda\\[15pt]
}\relax
\end{center}

\vfill

\phantom{a}







